---
title: "Project Al-Huda"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Al-Quran** - _An Introduction_

**Al-Quran** is the last holy book to have been revealed to mankind by Allah almighty.
It is known by many names and is revered by the entire Muslim world as the word of the Creator.
Prophet Muhammad (SAW) received this text through angel Jibrael (Gabriel) and it was later written by his companions.
It is the last divine book which was revealed to the last Prophet (SAW).
The revelation is in Arabic language and despite being 1400 years old it's language is still fresh and recognized.

The text is divided into 114 chapters known as Surahs.
These surahs are categorized as Meccan and Medinan based on their location of revelation to Prophet Muhammad (SAW). Furthermore the ayahs in surahs are grouped into rakus.

## Objectives

The goal of this project is to study Al-Quran from the perspective of a data scientist and explore the tools of R language along the way.

## Required Data

_**Al-Quran text**_

*   Obtained from [Al-Quran Cloud API](https://alquran.cloud/api).
The obtained files are in JSON formatand include metadata along with the required text. Further info can be obtained from referenced API endpoint.

In order to simplify, after reading the API documentation, I reduced the dataset and only included the following :

* Arabic Uthmani Text
* Simplified Arabic Text
* English Translation (Saheeh International)
* Surah list containing Surah metadata


## First Steps and Loading up Data

In order to load up JSON data as an R dataframe I used `jsonlite`. 

```{r include=FALSE}
library(dplyr)
library(jsonlite)
library(ggplot2)
```

Firstly lets load up the surah list into

```{r}
Surahs <- fromJSON("surat.json")
Surahs<-Surahs$surat # The actual data is in the sub-object "surat"
#fatiha<-Q[1]$surat[1]
```
We get surah list as `Surahs`. Let's see what does this variable contains.
```{r}
str(Surahs)
summary(Surahs)
```
The dataframe contains the following details :

*   `id`    -   the serial no of the surah from 1 to 114
*   `name`  -   the arabic name of the surah
*   `englishName`     -   English transliteration of `name`
*   `englishTranslation`    -   `name` translated into english
*   `revelationCity`    -   contains Meccan or Medinan
*   `numberOfAyats`     -   number of verses in the surah

Now is the time for data cleanup, however at the moment all I can think of is converting `revelationCity` to factor instead of char.
```{r}
Surahs$revelationCity<-as.factor(Surahs$revelationCity)
#str(Surahs)
```
## Plotting Surahs

```{r out.width="100%"}
ggplot(data=Surahs,aes(x=id,y=numberOfAyats,fill=revelationCity))+
  geom_bar(stat="identity")+
  #geom_text(aes(label=name), color="black", size=5.5)+
  theme_minimal()
```
This is our first plot. On the X-axis the `id` represents the ser no of the surahs from 1 to 114. On the Y-axis the `numberOfAyats` controls the bar height. The colors of the bars indicate `revelationCity`, either **Meccan** or **Medinan**.

This marks the end of first session. 