---
title: "Project Al-Huda"
output: html_document
---

> In continuation from [Session 2](https://rpubs.com/glasschakotra/huda2)


```{r setup, include=FALSE}

#knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(jsonlite)
library(wordcloud2)
library(tm)
library(extrafont)
```

# Word Clouds (Using Ayahs)

Have you wondered about the ayahs that have been repeated in the Quran?
Let's make a word cloud that shows repeating ayahs.

## 1. Loading Text

The `arabicAyahsSimple.json` file I prepared earlier will be used now.

We'll be using the Arabic Simplified version for the sake of simplicity.

```{r include=TRUE}
Arabic <- fromJSON("arabicAyahsSimple.json")$ayahs
# The required text is encapsulated in the `ayahs` object within every `json` file.

```
## 2. Preparing Ayah-Frequency Dataframes

Preparing a data frame `keyAyahs` by using R's built-in `table()` function that counts all occurrences of the text.
Then I convert it into a data frame using `as.data.frame()` function.
Finally I apply a filter to only select ayahs that have occurred at least twice.
Notice that now I'm using pipe operator `%>%` which makes life much easier.

Once the data frame is ready, it is ordered so the high `freq` ayahs are on top.

```{r out.width="100%"}
#Arabic<-filter(Arabic,surat_id>89) 
keyAyahs <- Arabic$text %>%
  table() %>%
  as.data.frame()%>%
  filter(Freq>1) 
keyAyahs$. <- as.character(keyAyahs$.)
names(keyAyahs)<-c("Ayah","Freq")
keyAyahs<-keyAyahs[order(-keyAyahs$Freq),]
```

## 3. Making The WordCloud

Had a whole night fighting with the `wordcloud2` function.
It turns out that the function omits higher frequency words to compensate for font-size.
Anyways the output is beautiful.
The most repeated ayah is from Surah Rehman and it is repeated 31 times.

```{r out.width="100%"}
# Colors inspired from : https://fromsystosys.netlify.app/2019/03/03/color-palettes-inspired-by-islamic-art/

cloud.colors = c("#301d25", "#7a4d41", "#275238","#9c1839","#6ab668","#59d0ee","#6767f4","#d6273b","#fffb49","#e69975","#5a4239","#8d332a")
cloud.background = "#d8cdbe"

wordcloud2(keyAyahs,
           color = rep_len(cloud.colors, nrow(keyAyahs)),
           backgroundColor = cloud.background,
           fontFamily = "Titr",
           size = .6,
           #minSize = 2,
           
           rotateRatio = 0)

```
